Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-24 ms.tex
more clean up, especially in introduction, and more notes to self

\begin{abstract}
We present full-sky maps of dust optical depth and temperature derived by 
fitting the \cite{FDS99} two-component dust emission model to
\PLANCK~217, 353, 545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the 
optical depth and temperature maps have angular resolution of $6.1'$. Such maps
 serve as an important alternative to and comparison for other dust 
emission models, especially the single modified blackbody (MBB) model in which 
$\beta$ and $T$ both vary spatially. We also expect the derived optical 
depth to provide valuable cross-checks for other dust-column related data 
products, specifically the \cite{SFD} map, which assumed 
$\beta = 2$ single-component dust emission and included a temperature map of 
inferior $\sim$$1.3^{\circ}$ resolution. We briefly compare our 
best-fit two-component spectral energy distributions to those of the 
\cite{planckdust} single-component parametrization.
%mention the enhanced temperature resolution relative to SFD
%Our optical depth map will also provide a useful reference for dust maps 
%based on stellar colors rather than infrared emission.
\end{abstract}

@@

%basic background about interstellar dust emission
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. The \textit{Infrared Astronomy 
Satellite} (\IRAS), with its $\sim$4$'$ resolution, revolutionized the study of
 Galactic dust emission, first revealing the high-latitude ``infrared cirrus'' 
using 60$\mu$m and 100$\mu$m observations \citep{low84, wheelock94}. Later, the
Diffuse Infrared Background Experiment (DIRBE) aboard the \COBE~satellite 
provided complementary full-sky measurements at ten infrared wavelengths from 
1.25$\mu$m to 240$\mu$m with inferior 0.7$^{\circ}$ angular resolution, but 
with a reliable zero point \citep{boggess92}. \COBE/FIRAS \citep{firas} also 
provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 narrow
frequency bins between 200 GHz and 2100 GHz.

\cite{FDS99} (hereafter FDS99) used FIRAS data to derive a globally best-fit 
model of dust emission applicable over a very broad range of frequencies. 
FDS99 showed that a model consisting of a single MBB with power law index 
$\beta$ could not accurately match the \IRAS/FIRAS/DIRBE spectrum at both the 
Wien and Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 
proposed a dust emission model consisting of two MBBs, each with a different
temperature and power law index. Physically, these two components
represent distinct dust grain species within the ISM, specifically 
amorphous silicates and carbonaceous grains.

re
The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and \IRAS~100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust spectral energy distribution (SED) composed
 of \PLANCK~and \IRAS~data. In doing so, we obtain $6.1'$ resolution maps of 
dust temperature and optical depth. Because we employ a model that has been 
validated with FIRAS data down to sub-mm wavelengths, we expect our best-fit 
parameters to be useful in constructing high-resolution predictions of dust 
emission over a very broad range of wavelengths. This includes low frequencies 
($<$350 GHz), which \cite{planckdust} caution their model may not adequately 
fit, and also measurements near the peak of the dust SED, for example 
\AKARI~140-160$\mu$m \citep{akari}. We also anticipate our derived optical 
depth map will serve as a useful comparison for extinction estimates based 
directly upon optical/NIR observations of stars.

@@

In $\S$\ref{sec:data} we discuss the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the data to isolate 
thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we describe the 
dust emission model we fit to the \PLANCK~and \IRAS~data. In 
$\S$\ref{sec:fitting} we provide details of the Markov chain Monte Carlo method
with which we have estimated the parameters of our model. In 
$\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
optical depth thus obtained, and conclude in $\S$\ref{sec:conclusion}.

@@

At each sky location, our baseline fit at the full $6.1'$ resolution 
incorporates only five independent intensity measurements (\verb|i100| along 
with the four highest-frequency \PLANCK~bands). FDS99 found typical values for 
$T_2$ and

@@

>>>>

\begin{abstract}
We present full-sky, $6.1'$ resolution maps of dust optical depth and 
temperature derived by fitting the \cite{FDS99} two-component dust emission 
model to \PLANCK~217, 353, 545, and 857 GHz, along with \cite{SFD} 
\IRAS~100$\mu$m data. These maps serve as an important alternative to and 
point of comparison for other dust emission models, especially the single 
modified blackbody model in which both the emissivity power law index and dust 
temperature vary continuously. We also expect the derived optical depth to 
provide valuable cross-checks for other dust-column related data products, 
specifically the \cite{SFD} map, which assumed a single modified blackbody 
with $\nu^2$ emissivity and included a temperature map of inferior 
$\sim$$1.3^{\circ}$ resolution. We compare our best-fit two-component spectral 
energy distributions to those of the \cite{planckdust} single-component 
parametrization.
%MENTION USE IN MAKING IR FOREGROUND PREDICTIONS
%mention more explicitly the enhanced temperature resolution relative to SFD??
%Our optical depth map will also provide a useful reference for dust maps 
%based on stellar colors rather than infrared emission.
\end{abstract}

@@

%basic background about interstellar dust emission
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. The \textit{Infrared Astronomy 
Satellite} (\IRAS), with its $\sim$4$'$ resolution, revolutionized the study of
 Galactic dust emission, first revealing the high-latitude ``infrared cirrus'' 
using 60$\mu$m and 100$\mu$m observations \citep{low84, wheelock94}. Later, the
Diffuse Infrared Background Experiment (DIRBE) aboard the \COBE~satellite 
provided complementary full-sky measurements at ten infrared wavelengths from 
1.25$\mu$m to 240$\mu$m with inferior 0.7$^{\circ}$ angular resolution, but 
with a reliable zero point \citep{boggess92}. \COBE/FIRAS \citep{firas} also 
provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 narrow
frequency bins between 30 GHz and 2850 GHz.

\citet[hereafter FDS99]{FDS99} used FIRAS data to derive a globally best-fit 
model of dust emission applicable over a very broad range of frequencies. 
FDS99 showed that no model consisting of a single modified blackbody (MBB) 
could accurately match the \IRAS/FIRAS/DIRBE spectrum at both the Wien and 
Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 therefore 
proposed a dust emission model consisting of two MBBs, each with a different 
temperature and power law index. Physically, these two components might 
represent distinct dust grain species within the ISM, namely amorphous 
silicates and carbonaceous grains.

% FDS used 100 GHz to 3000 GHz in their two-component fits
%mention which grain species is large vs. small

% should mention somewhere (probably in above paragraph, the range of
% frequencies over which FDS99 model was shown to be applicable

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and \IRAS~100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative parametrization for the dust spectral energy distribution 
(SED) composed  of \PLANCK~and \IRAS~data. In doing so, we obtain $6.1'$ 
resolution maps of dust temperature and optical depth. Because we employ a 
model that has been validated with FIRAS data down to sub-mm wavelengths, we 
expect our best-fit parameters to be useful in constructing high-resolution 
predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also measurements near the peak of the dust 
SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
derived optical depth map will serve as a useful comparison for extinction 
estimates based directly upon optical/NIR observations of stars. % and as
% a baseline or a next generation dust extinction map incorporating
% high resolution, fulls-sky infrared data sets such as WISE and Akari.

@@

In $\S$\ref{sec:data} we introduce the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the \PLANCK~maps to 
isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
describe the dust emission model we fit to the \PLANCK~and \IRAS~data. In 
$\S$\ref{sec:fitting} we provide details of the Markov chain Monte Carlo (MCMC)
 method with which we have estimated the parameters of our model. In 
$\S$\ref{sec:results} we present the full-sky maps of dust temperature and 
optical depth thus obtained, and conclude in $\S$\ref{sec:conclusion}.

@@

%the below statements seem like they might best be moved to a generic
%opening of the next section, stating our philosophy of breaking sky
%into pixels, each with 5 SED measurements, and that with this small
%number of constraints per pixel, it makes sense to have a baseline
% fit at full resolution that has only two free parameters
At each sky location, our baseline fit at the full $6.1'$ resolution 
incorporates only five independent intensity measurements (\verb|i100| along 
with the four highest-frequency \PLANCK~bands). FDS99 found typical values for 
$T_2$ and

@@

% maybe have a section justifying the T2 prior value of 16.2K, presumably using
% FIRAS as a cross-check?
